---
title: "Reed question"
output: html_notebook
---

Three out of 8 cells give positive to a treament (this is his control). How many samples does he have to test from another strain to make sure that there is no response (prob success = 0?


Power for different choices of n, assuming that πa = 0.55 and α = 0.05.

```{r}
enn = 1:2000
critical = qbinom(.025, enn, 0.5)
beta = pbinom(enn-critical,enn,.55) - pbinom(critical-1,enn,.55) 
xyplot(1-beta ~ enn, type="l", lwd=0.5, xlab="n", ylab="power")
```

Power of binomial distribution for different choices of n, assuming that probability of success are πα = 0, π0 = 3/8 and α = 0.01 (two tail).

```{r}
succ_control = 3/8
succ_new_exp = 0
my_x_range = c(1,20)
enn = 1:my_x_range[2]
alpha = 0.005

critical = qbinom(p = alpha, size = enn, prob = succ_control)
beta = pbinom(q = enn-critical,size = enn,prob = succ_new_exp) - pbinom(critical-1,enn,succ_new_exp) 
my_title = paste0("Psucc_cont=",succ_control,"; Psucc_alt=",succ_new_exp,"; alpha=",alpha)

p <- xyplot(1-beta ~ enn, type="l", lwd=1, xlab="n", ylab="power", scales = list(x=list(at = seq(my_x_range[1],my_x_range[2],1))), main = my_title, abline=c(h=0.8))
#ggsave2(filename = "~/Documents/LOCAL_PROJECTS/REED/Binomial_power/power_analysis_p0.pdf", plot = p)
pdf(file = "~/Documents/LOCAL_PROJECTS/REED/Binomial_power/power_analysis_p0.pdf")
  print(p)
dev.off()
print(p)
```

Power of binomial distribution for different choices of n, assuming that probability of success are πα = 0.1, π0 = 3/8 and α = 0.01 (two tail).

```{r}
succ_control = 3/8
succ_new_exp = 0.1
my_x_range = c(1,50)
enn = 1:my_x_range[2]
alpha = 0.005

critical = qbinom(p = alpha, size = enn, prob = succ_control)
beta = pbinom(q = enn-critical,size = enn,prob = succ_new_exp) - pbinom(critical-1,enn,succ_new_exp) 
my_title = paste0("Psucc_cont=",succ_control,"; Psucc_alt=",succ_new_exp,"; alpha=",alpha)

p01 <- xyplot(1-beta ~ enn, type="l", lwd=1, xlab="n", ylab="power", scales = list(x=list(at = seq(0,my_x_range[2],2))), main = my_title, abline=c(h=0.8)) 
pdf(file = "~/Documents/LOCAL_PROJECTS/REED/Binomial_power/power_analysis_p01.pdf")
  print(p01)
dev.off()
print(p01)
```

Power of binomial distribution for different choices of n, assuming that probability of success are πα = 0.1, π0 = 3/8 and α = 0.01 (two tail).

```{r}
succ_control = 3/8
succ_new_exp = 0.2
my_x_range = c(1,100)
enn = 1:my_x_range[2]
alpha = 0.005

critical = qbinom(p = alpha, size = enn, prob = succ_control)
beta = pbinom(q = enn-critical,size = enn,prob = succ_new_exp) - pbinom(critical-1,enn,succ_new_exp) 
my_title = paste0("Psucc_cont=",succ_control,"; Psucc_alt=",succ_new_exp,"; alpha=",alpha)

p02 <- xyplot(1-beta ~ enn, type="l", lwd=1, xlab="n", ylab="power", scales = list(x=list(at = seq(0,my_x_range[2],5))), main = my_title, abline=c(h=0.8)) 
pdf(file = "~/Documents/LOCAL_PROJECTS/REED/Binomial_power/power_analysis_p02.pdf")
  print(p02)
dev.off()
print(p02)
```

